Notes and Problems from My Research\vspace{-1ex}

### 2019-01-10 Hopf Algebra Notes/Hopf Algebras.tex
update notes

%set up theorem/definition/etc envs
%Problems will be created using their own counter and style
\theoreminframepreskip{0pt}
\theoreminframepostskip{0pt}
\newframedtheorem{prob}{Problem}[section]

@@

\begin{conj}[Etingof-Ostrik `04]
	If $A$ is a finite dimentional Hopf algebra, then 
	\[\bigoplus_{i\ge 0}\Ext_A^i(k,k)\]
	is Noetherian.
\end{conj}

@@

\begin{lem}
	The following are equivalent:
	\begin{enumerate}
		\item $V$ is an algebra object in $\Coalgk$
		\item $V$ is a coalgebra object in $\Algk$
		\item There are morphisms $m,u,\Delta,\varepsilon$ such that
		\begin{itemize}
			\item $(V,m,u)$ is an algebra
			\item $(V,\Delta,\varepsilon)$ is a coalgebra
			\item Equivalently:
			\begin{itemize}
				\item $m$ and $u$ are coalgebra morphisms
				\item $\Delta$ and $\varepsilon$ are algebra morphisms.
			\end{itemize}
		\end{itemize}
	\end{enumerate}
\end{lem}
\begin{prf}
	The nice thing here is that the $(a)\Leftrightarrow (c)$ without the last condition. A similar fact holds
	for $(b)$ except the second-to-last. The last thing to do is to prove the last two conditions are equivalent.
\end{prf}
\begin{prob}
	Fill in the details for the proof above.
\end{prob}

@@

\begin{prob}
	\begin{enumerate}
		\item Suppose that $\ch k\ne 2$. Classify all bialgebras of $\dim 2.$
		\item Do the same for $\ch k = 2.$
	\end{enumerate}
\end{prob}
\begin{sol}
	\subsubsection*{Part (a)}
	Consider $\varepsilon:V\to k$ and consider $\ker\varepsilon\lhd V$. Since $\varepsilon$ cannot be the zero map,
	$\ker\varepsilon=kx$ for some $x\in V\setminus 0$. 
\end{sol}

>>>>

%set up theorem/definition/etc envs
%Problems will be created using their own counter and style
\theoremstyle{break}
\theoreminframepreskip{0pt}
\theoreminframepostskip{0pt}
\newframedtheorem{prob}{Problem}[section]

@@

\begin{conj}[Etingof-Ostrik `04]
	If $A$ is a finite dimentional Hopf algebra, then 
	\[\bigoplus_{i\ge 0}\Ext_A^i(_Ak, _Ak)\]
	is Noetherian.
\end{conj}

@@

\begin{lem}
	The following are equivalent:
	\begin{enumerate}
		\item $V$ is an algebra object in $\Coalgk$
		\item $V$ is a coalgebra object in $\Algk$
		\item There are morphisms $m,u,\Delta,\varepsilon$ such that
		\begin{itemize}
			\item $(V,m,u)$ is an algebra
			\item $(V,\Delta,\varepsilon)$ is a coalgebra
			\item Equivalently:
			\begin{itemize}
				\item $m$ and $u$ are coalgebra morphisms
				\item $\Delta$ and $\varepsilon$ are algebra morphisms.
			\end{itemize}
		\end{itemize}
	\end{enumerate}
\end{lem}
\begin{prf}
	The nice thing here is that the $(a)\Leftrightarrow (c)$ without the last condition. A similar fact holds
	for $(b)$ except the second-to-last. The last thing to do is to prove the last two conditions are equivalent.
\end{prf}
\begin{prob}
	Fill in the details for the proof above.
\end{prob}
\begin{sol}
	Assume that $(V,m,u,\Delta,\varepsilon)$ is an algebra and coalgebra and further that
	$m$ and $u$ are coalgebra morphisms. That means in particular that the diagrams in figure \ref{fig-coalg-mor} commute.
	\begin{figure}[h]\label{fig-coalg-mor}
		\centering
		\begin{tikzcd}
			V\otimes V \ar[d,swap,"\Delta\otimes\Delta"]\ar[r,"m"] & V\ar[r,"\Delta"] & V\otimes V\\
			V^{\otimes 4}\ar[rr,"T_{2,3}"] & & V^{\otimes 4}\ar[u,swap,"m\otimes m"]
		\end{tikzcd}
		\begin{tikzcd}
			k\ar[r,"\Delta"]\ar[d,"u"] & k\otimes k\ar[d,"u\otimes u"]\\
			V\ar[r,"\Delta"] & V\otimes V
		\end{tikzcd}
		\label{fig-coalg-mor}
		\caption{$m$ and $u$ are coalgebra morphisms.}
	\end{figure}

	We are looking to prove that $\Delta$ and $\varepsilon$ are algebra morphisms, or that 
	the diagrams in figure \ref{fig-coalg-mor}  commute.
	\begin{figure}[h]
		\centering
		\begin{tikzcd}
			V\otimes V\ar[r,"m"]\ar[d,"\Delta\otimes \Delta"] & V\ar[d,"\Delta"]\\
			V^{\otimes 4}\ar[r,"m"] & V\otimes V
		\end{tikzcd}
		\begin{tikzcd}
			V\otimes V\ar[r,"\varepsilon\otimes\varepsilon"]\ar[d,"m"] & k\otimes k\ar[d,"m"]\\
			V\ar[r,"\varepsilon"] & k
		\end{tikzcd}
		\label{fig-alg-mor}
		\caption{$\Delta$ and $\varepsilon$ are algebra morphisms.}
	\end{figure}

	From here it's actually a bit boring because it's kinda just a definition/notation game.
	It boils down to the fact that the (co)multiplication on $V\otimes V$ has a twist that 
	exactly lines up so that each square is saying the same thing.
\end{sol}

@@

\begin{prob}
	\begin{enumerate}
		\item Suppose that $\ch k\ne 2$. Classify all bialgebras of $\dim 2.$
		\item Do the same for $\ch k = 2.$
	\end{enumerate}
\end{prob}
\begin{sol}
	\subsubsection*{Part (a)}
	Consider $\varepsilon:V\to k$ and consider $\ker\varepsilon\lhd V$. By rank-nullity, $\dim\ker\varepsilon= 1$, so
	$\ker\varepsilon=kx$ for some $x\in V$. Therefore $x^2=cx$ for some $c$, and if $c=0$, then (as an algebra) $V\cong k[x]/(x^2)$.
	Otherwise consider $y=\frac{x}{c}$. In this case $y^2=\frac{x^2}{c^2}=\frac{x}{c}=y$, and $V\cong k[x]/(x^2-x)$.

	Notice that in either case $\varepsilon(x)=0$, so let
	\[\Delta(x)=a(1\otimes 1)+b(1\otimes x)+c(x\otimes 1) + d(x\otimes x)\]
	and using that $\varepsilon\otimes \id\circ\Delta=\id\otimes\varepsilon\circ\Delta$
	and that each should be (essentially) the identity (this is just the diagram we saw before),
	we get $a=0$ and $b=c=1$. Thus the coalgebra structure of any Hopf algebra is given by 
	\[\varepsilon(x)=0,\quad \Delta(x)=1\otimes x+x\otimes 1+d(x\otimes x).\]

	Consider first the case when $x^2=0$. Then since comultiplication will be an algebra morphism,
	\[0=\Delta(x^2)=\Delta(x)^2=1\otimes x^2+x^2\otimes 1+d^2(x^2\otimes x^2)+2(x\otimes x)+2d(x\otimes x^2)+2d(x^2\otimes x)\]
	and since $x^2=0$, 
	\[0=2(x\otimes x).\]
	But $x\otimes x$ is a basis element of $V\otimes V$, so $V$ can only have this algebra structure
	when $\ch k=2$. We will return to this in the next part.

	So then $x^2=x$ and using the computation above,
	\[1\otimes x+x\otimes 1+d(x\otimes x)=\Delta(x)=\Delta(x^2)=1\otimes x+x\otimes 1+(d^2+4d+2)(x\otimes x)\]
	so
	\[(d^2+3d+2)(x\otimes x)=0\quad\Rightarrow\quad d^2+3d+2=(d+2)(d+1)=0\]
	and so either $d=-1$ or $d=-2$.

	One can verify that $\Delta$ is coassociative, so we can conclude that when $\ch k\ne 2$, 
	there are precisely two Hopf algebra structures with algebra structure $k[x]/(x^2-x)$ and
	comultiplication either
	\[\Delta(x)=1\otimes x+x\otimes 1-x\otimes x\quad\text{or}\quad \Delta(x)=1\otimes x+x\otimes 1-2(x\otimes x)\]

	\subsection*{(b)}
	Now assume that $\ch k=2$ and that $V\cong k[x]/(x^2-x)$ as an algebra. Then using the analysis above, 
	we see that we can choose comultiplication either
	\[\Delta(x)=x\otimes 1+1\otimes x\quad\text{or}\quad \Delta(x)=1\otimes x+x\otimes 1+x\otimes x.\]

	If instead $V\cong k[x]/(x^2)$, then \textit{any} value of $d$ will suffice, so there are a full $k$'s worth
	of Hopf algebra structures that can appear.
\end{sol}

\section{January 9, 2019}
Today we are going to rely heavily on Sweedler notation. :) Notice that if we are looking at actual objects in the 
diagram for coassociativity, we get
\begin{figure}[h]
	\centering
	\begin{tikzcd}
		v\ar[r]\ar[d] & \sum v_{(1)}\otimes v_{(2)}\ar[d]\\
		\sum v_{(1)}\otimes v_{(2)}\ar[r] & \sum (v_{(1)})_{(1)}\otimes (v_{(1)})_{(2)}\otimes v_{(2)}=\sum v_{(1)}\otimes (v_{(2)})_{(1)}\otimes (v_{(2)})_{(2)}
	\end{tikzcd}
	\caption{Coassociativity on elements in Sweedler notation}
\end{figure}

\begin{ex}
	Let $G$ be a group and $kG$ be the group algebra. The algebra structure arises as normal
	where $g\cdot h$ comes from the structure on $G$. Then $\Delta(g)=g\otimes g$ and this extends linearly.

	But then if you consider $\Delta(\sum c_gg)$, notice that by the nature of tensors this is not unique!
	So we will just write
	\[\Delta\left(\sum c_gg\right)=\sum_Gc_g(g\otimes g)=\sum v_{(1)}\otimes v_{(2)}\]
\end{ex}

\subsection{Algebra structure on $V\otimes V$}
We said earlier on that $\Algk$ is a symmetric \textit{tensor} category. But how do we
define the multiplication on the tensor product?

Well it all comes from the twist! We define
\[m_{V\otimes W}=(m_V\otimes m_W)\circ(\id_V\otimes \tau_{2,3}\otimes \id_W)\]
where $\tau_{2,3}$ is the twist morphism.

More simply, $u_{V\otimes W}:k=k\otimes k\to V\otimes V$ simply defined by $u_V\otimes u_W$.

So then when we say that $\Delta$ is an algebra morphism, we are saying that for all $v,w\in V$
\[\Delta(vw)=\sum(vw)_{(1)}\otimes(vw)_{(2)}=(\sum v_{(1)}\otimes v_{(2)})(\sum w_{(1)}\otimes w_{(2)})=\sum v_{(1)}w_{(1)}\otimes v_{(2)}w_{(2)}\]

\subsection{Hopf Algebras}
Already to the good stuff!
\begin{defn}
	$V\in\Vectk$ is a \textbf{Hopf algebra} if $V$ is a bialgebra together with an \textbf{antipode}
	$S:V\to V$ satisfying
	\[(S,\id_V)\circ \Delta=\varepsilon=(\id_V,S)\circ\Delta\]
\end{defn}
\begin{conj}
	If $V\in\Vectk$ is a Noetherian Hopf algebra, then $S$ is bijective.
\end{conj}

\subsection{History and Motivation}
Hopf himself was a topologist, so this is the first context in which it arose. In the 1940's,
he began studying Hopf algebras over $\Z_2$ graded $k$ vector spaces. For instance, the 
cohomology ring of topological space $X$ with coefficients in $k$.

Later, in combinatorics, they ended popping up. Looking at rings of symmetric functions and other places
gave some interesting examples.

Then in group theory you can define a functor from groups to Hopf algebras by $F(G)=kG$
with the diagonal map. The antipode is just the inverse.

Then with Lie algebras, you can look at $\mathcal{U}(L)$, the universal enveloping algebra is a Hopf algebra.

Finally with algebraic groups (yay!) we take an algebraic group $G$ and consider the ring of functions on it, 
which is again a Hopf algebra.

Some ``cousins'' of Hopf algebras: quasi, weak, multiplier, ribbon, quasi-triangular, etc Hopf algebras. 
Each has slightly different base category or restrictions.

### 2019-01-10 Lie Algebra Notes/Lie Algebras.tex
update notes

%Lie algebra stuff
\DeclareMathOperator{\gl}{\mathfrak{gl}}
\let\sl\relax
\DeclareMathOperator{\sl}{\mathfrak{sl}}
\DeclareMathOperator{\tr}{tr}

@@

Given $V=k^n$ and a bilinear form on $V$, we can look at all $X\in \gl(n,k)=\gl(V)$ such that 
$(Xv,w)=(v,Xw)$. Then $X$ is \textbf{skew-adjoint} with respect to the form. One can check that 
$[XY]$ is skew-adjoint whenever both $X$ and $Y$ are.

\subsection{Generating (skew) symmetric forms}
It ends up that the dot product (which a symmetric form) is misleadingly simple -- thus
we will look elsewhere.

@@

We will make a particular choice for our matrix $M$ and then study the resulting
Lie algebras in much more detail next time. The choices will be: 
\begin{itemize}
	\item For type $D_m$:
	\[\begin{pmatrix}
		0 & I_m\\
		I_m & 0
	\end{pmatrix}\]
	\item For type $C_m$:
	\[\begin{pmatrix}
		0 & -I_m\\
		I_m & 0
	\end{pmatrix}\]
	\item For type $B_m$:
	\[\begin{pmatrix}
		1 & 0 & 0\\
		0 & 0 & I_m\\
		0 & I_m & 0
	\end{pmatrix}\]
\end{itemize}
\end{document}

>>>>

%Lie algebra stuff
\DeclareMathOperator{\gl}{\mathfrak{gl}}
\let\sl\relax
\DeclareMathOperator{\sl}{\mathfrak{sl}}
\DeclareMathOperator{\so}{\mathfrak{so}}
\let\sp\relax
\DeclareMathOperator{\sp}{\mathfrak{sp}}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\ad}{ad}

@@

Given $V=k^n$ and a bilinear form on $V$, we can look at all $X\in \gl(n,k)=\gl(V)$ such that 
$(Xv,w)=(v,Xw)$. Then $X$ is \textbf{adjoint} with respect to the form. There is a similar definition for when
$X$ is \textbf{skew-adjoint.} One can check that 
$[XY]$ is skew-adjoint whenever both $X$ and $Y$ are.

\subsection{Generating (skew) symmetric forms}
It ends up that the dot product (which is a symmetric form) is misleadingly simple -- thus
we will look elsewhere.

@@

We will make a particular choice for our matrix $M$ and then study the resulting
Lie algebras in much more detail next time. The choices will be: 
\begin{itemize}
	\item For type $D_m$:
	\[\begin{pmatrix}
		0 & I_m\\
		I_m & 0
	\end{pmatrix}\]
	\item For type $C_m$:
	\[\begin{pmatrix}
		0 & -I_m\\
		I_m & 0
	\end{pmatrix}\]
	\item For type $B_m$:
	\[\begin{pmatrix}
		1 & 0 & 0\\
		0 & 0 & I_m\\
		0 & I_m & 0
	\end{pmatrix}\]
\end{itemize}

\section{January 9, 2019}
Today we will be looking deeply into the stucture of linear Lie algebras of types A-D.

\subsection{Linear Lie Algebras Revisited}
Recall that the \textbf{matrix unit} $e_{ij}$ is the matrix with 1 in the $(i,j)$ entry and 
zero elsewhere. And then $e_{ij}e_{kl}=\delta_{jk}e_{il}$ and furthermore
\[[e_{ij}e_{kl}]=\delta_{jk}e_{il}-\delta_{li}e_{kj}.\]
This is especially nice when $j=i$, called the \textbf{diagonal matrix unit}.

Then we look at type $A_{n-1}$ ($\sl(n,k)$). Let $D$ be the set of diagonal matrices in this algebra.
Notice the dimension is $n-1$ since then $n^{th}$ term on the diagonal is determined as the
negative of the sum of the other $n-1$ terms. Let $A=\operatorname{diag}(d_1,\dots,d_n)$. Then consider the eigenvalues
associated with $e_{ij}$: 
\[[Ae_{ij}]=(d_i-d_j)e_{ij}=(E_i-E_j)Ae_{ij}\]
where $E_i$ is the linear functional selecting the $i^{th}$ entry in $A$. Moreover, $D$ is abelian as a Lie algebra, so $D$
acts diagonally on $L=\sl(n,k)$ by commutation with eigenvalues $E_i-E_j$ and zero
for $1\le i,j\le n$ and $i\ne j$.

In the other classical cases B-D, there is always a matrix $M$ which defines the form $(v,w)=v^tMw$ 
as we saw yesterday. In all three cases, the Lie algebra exists consists of all skew-adjoint matrices
$X$ relative to the form. $B_m=\mathfrak{so}(2m+1,k)$ as well as $D_m=\mathfrak{so}(2m,k)$ and $C_m=\mathfrak{sp}(2m,k)$.

This condition translates to the form of matrices in the above Lie groups and the condition is always $Mx=-x^tM$ in all cases.

Type B:
\[\begin{pmatrix}
	0 & b_1 & b_2\\
	c_1 & m & n\\
	c_2 & p & q
\end{pmatrix}\]
where $c_1=-b_2^t$, $c_2=-b_1^t$, $q=-m^t$, $n^t=-n$ and $p^t=-p$.

Type C:
\[\begin{pmatrix}
	m& n\\ p & q
\end{pmatrix}\]
where $n^t=n, p^t=p,$ and $m^t=-q$.

Type D:
\[\begin{pmatrix}
	m& n\\ p & q
\end{pmatrix}\]
where $n^t=-n, p^t=-p,$ and $m^t=-q$.

Looking at the eigenvalues of elements of $D$ associated to vectors $e_{ij}-e_{m+i,m+j}$. Look at photos

Using a similar analysis, we can look at types $B$ and $D$. We define the functions $E_i$ similarly on the space of diagonalmatrices and gives a rise to the following collection of linear functions:
in $B_m:$ $\pm E_i$ and $\pm(E_i\pm E_j)$ and $D_m$ gives us $\pm(E_i\pm E_j)$.

This collection of functions in each case is called the \textbf{root system of the Lie algebra},
Then any complex simple finite-dimensional Lie algebra is classified by its root system.
The (perhaps surprising) fact is that this already encompasses all but finitely many of these
things up to ismorphism: the classical Lie algebras. Eventually we will learn more about the
\textbf{exceptional Lie groups.}

This section was a little hard to follow and the handling in Humphreys is easier to follow, 
but delays speaking about root systems and actually deriving the eigenfunctions (is that the right word?)
until significantly later. Monty seemed to think it was acceptable to delay the understanding of this a bit.

\subsection{Derivations and $\exp$}
Look an an arbitrary Lie algebra over a field $k$ where $\ch k=0$ (which we will mostly be assuming from here on)
. Let $\delta$ be a derivation of $L$, so that $[\delta x,y]+[x\delta y]=\delta[x,y]$. Assume that $\delta$ is nilpotent.

Then the ``power series'' (polynomial) is
\[\exp\delta=\sum_{i>0}\frac{\delta^i}{i!}\]
\begin{prob}
	This is a good exercise to go through: Check that
	\[[(\exp\delta)x,(\exp \delta)y)=[xy]\]
	for each $x,y\in L$
\end{prob}

\begin{rmk}
	This actually shows that $\exp\delta$ is an automorphism of $L$. Furthermore you'd find that
	\[(\exp\delta)(\exp(-\delta))=1.\]
\end{rmk}

What if $k=\R$ or $\C$? Then the power series (even when $\delta$ is not nilpotent!) always converges
and defines an automorphism as before.

\begin{lem}
	For all \textbf{complex} semisimple Lie algebras $L$ it turns out that the group
	generated by $\exp\ad x$ ($\ad x(y)=[xy]$) coincides with the group generated by all 
	nilpotent $\ad x$.
\end{lem}
\subsection{Adjoint group}
The last thing for today is to define the adjoint group:
\begin{defn}
	Let $L$ be a Lie algebra, then 
	\[\operatorname{Int}(L)=\exp\ad L\]
	is the \textbf{Adjoint group} of $L$. It is a subgroup (so we believe) of the Lie
	Group associated to $L$.
\end{defn}

Some examples of adjoint groups:
\begin{itemize}
	\item If $L=\sl(n,\C)$, then $\operatorname{Int}(L)=PSL(n,\C)=SL(n,\C)/\text{center}$
	\item If $L=\so(n,\C)$, then $\operatorname{Int}(L)=PSO(n,\C)$
	\item If $L=\sp(2n,\C)$ then $\operatorname{Int}(L)=PSp(2n,\C)$.
\end{itemize}

\end{document}

### 2019-01-10 Reading Notes/reading_notes.tex
update notes

\part{Winter 2019}
This is my first official quarter as Julia's student! My plan for now is to continue working on Waterhouse as well
as learn about algebraic geometry (alongside my usual classes, of course).
\section{Affine Group Schemes (Waterhouse)	}
To give a sense of direction, Julia recommended that I take a look at the following regularity theorem:
\begin{thm}[Smoothness Theorem]\label{smooth}
	Let $G$ be an algebraic affine group scheme over a field $k$. Then $k[G]\otimes \bar k$ is reduced if and
	only if $\dim G = \rank \Omega_{k[G]}$.
\end{thm}
I have quite a bit of information to process before this, so I will get started!
\begin{defn}[Closed Embedding]
	If $G$ and $H$ are affine group schemes represented by $A$ and $B$, respectively and
	if $\psi:H\to G$ is a homomorphism of affine group schemes (locally a group homomorphism)
	then if the corresponding algebra map $A\to B$ is surjective, then $\psi$ is called
	a \textbf{closed embedding.}
\end{defn}

@@

	When $M=\Z$, 
\end{prf}

@@

\subsection{Waterhouse}

>>>>

\part{Winter 2019}
\section{Preparation for the Quarter}
This is my first official quarter as Julia's student! My plan for now is to continue working on Waterhouse as well
as learn about algebraic geometry (alongside my usual classes, of course).
To give a sense of direction, Julia recommended that I take a look at the following regularity theorem:
\begin{thm}[Smoothness Theorem]\label{smooth}
	Let $G$ be an algebraic affine group scheme over a field $k$. Then $k[G]\otimes \bar k$ is reduced if and
	only if $\dim G = \rank \Omega_{k[G]}$.
\end{thm}
\section{Affine Group Schemes (Waterhouse and Jantzen)	}
I have quite a bit of information to process before this, so I will get started!
\begin{defn}[Closed Embedding]
	If $G$ and $H$ are affine group schemes represented by $A$ and $B$, respectively and
	if $\psi:H\to G$ is a homomorphism of affine group schemes (locally a group homomorphism)
	then if the corresponding algebra map $A\to B$ is surjective, then $\psi$ is called
	a \textbf{closed embedding.}
\end{defn}

@@

	When $M=\Z$, $k[M]\cong k[X,X^{-1}]$, so $G= \Gm$\footnote{Notice that here Waterhouse also
	uses that the basis elements $e_i$ are group-like and so $\Delta(e_i)=e_i\otimes e_i$. I am not
	quite sure why this is necessary.} Similarly if $M=\Z/n$ then $G\cong \mun{n}$
\end{prf}

Looking at my progress over the last several days, I am thinking that I am getting
too much in the weeds writing out all the lemmas and proofs. Perhaps it is better to read more quickly
and only take note of theorems as I need/use them.

\subsection{Cartier Duals}
The gist here is that if $G$ is represented by $A$, then we can define the dual 
$A^D=\Hom(A,k)$ and then $A^D$ represents a new scheme $G^D$ called the \textbf{Cartier Dual.}

We do some work to show that, in fact, elements of $G^D$ are in correspondence with the 
group-like elements of $A$, or equivalently the character group of $G$, $X_G$.

It is easy enough to evaluate $G^D(k)\cong\Hom(A^D,k)$, but luckily one shows that
``dualizing'' commutes with tensor products (and thus with extension of scalars) and $\Hom$. Thus
if $G_R$ is the scheme represented by $A\otimes_k R$, then using that $\Hom_k(A^D,R)\cong\Hom_R(A^D\otimes R,R)$,
\[G^D(R)=(G^D)_R(R)\]
which is represented by $(A\otimes R)^D=A^D\otimes R$, so finally 
\[G^D(R)=(G_R)^D(R)=\{\text{group-like elements in }A\otimes_k R\}\cong \Hom(G_R,(\Gm)_R)\]

@@

\subsection{Waterhouse}
\begin{wprob}{2.1}
	\begin{enumerate}
		\item Show that there are no nontrivial homomorphisms from $\Gm$ to $\Ga$.
		\item If $k$ is reduced, show that there are no nontrivial homomorphisms from $\Ga$ to $\Gm$.
		\item For each nonzero $b\in k$ with $b^2=0$, find a nontrivial homomorphism $\Ga\to\Gm$.
	\end{enumerate}
\end{wprob}
Hmm, there must be a small bug in my macro but I can't find it. I get an error about \texttt{missing `\textbackslash item'}
in the definition below. It seems to only occur when I use \texttt{\textbackslash subsubsection*} and the like.

\begin{sol}
	\subsubsection*{(a)}
	Let $\Phi:\Gm\to\Ga$ and let $\varphi:k[X]\to k[X,X^{-1}]$ be the corresponding Hopf
	algebra map. But then we have that 
	\[\varphi\otimes\varphi \circ \Delta_a(X)=\Delta_m\circ\varphi(X)\]
	and so using that $\Delta_m(a)=a\otimes a$ and $\Delta_a(b)=b\otimes1+1\otimes b$, we get
	\[\varphi(X)\otimes\varphi(1)+\varphi(1)\otimes\varphi(X)=\varphi(X)\otimes\varphi(X)\]

\end{sol}
